NLO QCD+EW corrections to diphoton production in association with a vector boson

### 2017-10-19 intro.tex
updates

The precise understanding of the electroweak symmetry breaking mechanism is an important cornerstone in verifying the
Standard Model. Different realizations of the electroweak sector or new physics coupling to electroweak gauge bosons will
yield to deviations compared to the Standard Model prediction. New physics effects can conveniently be described in terms
of an effective theory where new heavy degrees of freedom are integrated out and deviations from the Standard Model are 
parametrised by higher dimensional operators \cite{Weinberg:1978kz,Weinberg:1979pi}. Higher dimensional operators can lead
 to deviations in triple and quartic gauge couplings. Moreover, new vertices (e.g. $Z\gamma\gamma$) that do not exist in the 
Standard Model can appear. The class of processes that involve a pair of photons in association with another vector boson
allows to measure deviations in triple and quartic gauge couplings and is therefore a particularly interesting class of processes.
 Consequently both ATLAS and CMS have measured these type of processes und derived constraints on anomalous gauge
 couplings \cite{Aad:2016sau,Sirunyan:2017lvq,Aad:2015uqa,Aad:2015bua}

>>>>

The precise understanding of the electroweak symmetry breaking 
mechanism is an important cornerstone of the LHC physics 
programme. 
Different realisations of the electroweak sector or new physics 
coupling to electroweak gauge bosons will yield to deviations 
compared to the Standard Model prediction. 
New physics effects can conveniently be described in terms of 
an effective theory where new heavy degrees of freedom are 
integrated out and deviations from the Standard Model are 
parametrised by higher dimensional operators 
\cite{Weinberg:1978kz,Weinberg:1979pi}. 
Higher dimensional operators can lead to deviations in triple 
and quartic gauge couplings. Moreover, new vertices 
(e.g. $\gamma\gamma\gamma$, $Z\gamma\gamma$) that do not 
exist in the Standard Model can appear. 
The class of processes that involve a pair of photons in 
association with another vector boson allows to measure 
deviations in triple and quartic gauge couplings and is 
therefore a particularly interesting class of processes. 
Consequently both ATLAS and CMS have measured these types of 
processes and derived constraints on anomalous gauge couplings 
\cite{Aad:2016sau,Sirunyan:2017lvq,Aad:2015uqa,Aad:2015bua}.

In this paper we calculate the next-to-leading order QCD and 
electroweak corrections to the processes $\gamma\gamma\gamma$, 
$\gamma\gamma e^{+} e^{-}$ and $\gamma\gamma e^{-} \bar{\nu_e}$. 
For the latter two, all possible off-shell contributions of 
intermediate vector bosons are taken into account. 
The QCD corrections to these processes have already appeared 
in the literature 
\cite{Bozzi:2011en,Campbell:2012ft,Bozzi:2011wwa}. 
For a more complete picture of the higher order effects we 
recompute them for a centre of mass energy of 
13\,TeV, and supplement them with the next-to-leading order 
electroweak corrections. 
Although the electroweak corrections are much smaller at the level 
of the total cross section compared to the NLO QCD corrections 
they are particularly important when deriving limits on 
anomalous couplings. 
The effects of higher dimensional operators increase in the 
high energy tails of differential distributions and lead to a 
change of the shapes. And it is in the same region where the 
Sudakov logarithms from the electroweak corrections will play 
an essential role as well.

The paper is organized as follows. 
In Section \ref{sec:setup} we describe the calculational setup 
that has been used to obtain our numerical result which we are 
going to discuss in Section \ref{sec:results} before we 
conclude in Section \ref{sec:conclusions}.

### 2017-10-19 results.tex
updates

@@

>>>>

We use the \textsc{CT14nlo} PDF set with $\alpha_s(m_Z)=0.118$. 
The use of a QCD-only PDF is justified by the fact that, 
at LO, the photon induced corrections are negligible.

We define our central scales through
\begin{equation}
  \label{eq:murfdef}
  \begin{split}
    \muR^0 = \muF^0 = \ldots
  \end{split}
\end{equation}
and subsequently vary them by the conventional factor 
of two to estimate higher order contributions.

@@

\begin{table}[h!]
  \centering
  \begin{tabular}{l||c|c|c}
      & $\;\;pp \to \gamma \gamma\gamma\;\;$
      & $\;\;pp \to \gamma \gamma e^-\bar\nu_e\;\;$ 
      & $\;\;pp \to \gamma \gamma e^+e^-\;\;$ \\
    \hline\hline
    $\sigma_\text{LO}\;\;[\text{pb}] $ &  &  & \\
    \hline
    $\delta_\text{QCD}\;\;[\text{pb}]\;\;\pTveto=\infty $ &  &  & \\
    \hline
    $\delta_\text{QCD}\;\;[\text{pb}]\;\;\pTveto=30\,\text{GeV} $ &  &  & \\
    \hline
    $\delta_\text{EW}\;\;[\text{pb}] $ &  &  & \\
  \end{tabular}
  \caption{
    Total cross sections at LO, NLO QCD and NLO EW for $\gamma\gamma\gamma$, 
    $\gamma\gamma e^-\bar\nu_e$ and $\gamma\gamma e^+e^-$
    production at 13\,TeV at the LHC.
    \label{tab:xsec}
  } 
\end{table}

### 2017-10-19 setup.tex
updates

We define our central scales through
\begin{equation}
  \label{eq:murfdef}
  \begin{split}
    \muR^0 = \muF^0 = \ldots
  \end{split}
\end{equation}
and subsequently vary them by the conventional factor 
of two to estimate higher order contributions.

\begin{figure}[t!]
  \begin{tabular}{ccccc}
    \includegraphics[width=0.288\textwidth]{diagrams/aaa_V_2} & &
    \includegraphics[width=0.288\textwidth]{diagrams/aaa_V_1} & &
    \includegraphics[width=0.288\textwidth]{diagrams/aaa_V_3} \\
  \end{tabular}
  \caption{
    Sample diagrams of electroweak virtual corrections to triple 
    photon production.
  }
\end{figure}

\begin{figure}[t!]
  \begin{tabular}{ccccc}
    \includegraphics[width=0.288\textwidth]{diagrams/aaW_V_2} & &
    \includegraphics[width=0.288\textwidth]{diagrams/aaW_V_1} & &
    \includegraphics[width=0.288\textwidth]{diagrams/aaW_V_3} \\
  \end{tabular}
  \caption{
    Sample diagrams of electroweak virtual corrections to diphoton 
    production in association with a lepton-neutrino pair.
  }
\end{figure}

\begin{figure}[t!]
  \begin{tabular}{ccccc}
    \includegraphics[width=0.288\textwidth]{diagrams/aaZ_V_2} & &
    \includegraphics[width=0.288\textwidth]{diagrams/aaZ_V_1} & &
    \includegraphics[width=0.288\textwidth]{diagrams/aaZ_V_3} \\
  \end{tabular}
  \caption{
    Sample diagrams of electroweak virtual corrections to diphoton 
    production in association with a lepton-pair.
  }
\end{figure}

>>>>

A selection of one-loop amplitudes contributing to the three 
considered processes are shown in Figures 
\ref{fig:aaa:amps}--\ref{fig:aaz:amps}. 
The highest point loop integrals occuring in $\gamma\gamma\gamma$ 
production are pentagons, while both $\gamma\gamma e^-\bar\nu_e$ 
and $\gamma\gamma e^+e^-$ productions include up to hexagons at 
NLO EW.

\begin{figure}[t!]
  \begin{tabular}{ccccc}
    \includegraphics[width=0.288\textwidth]{diagrams/aaa_V_2} & &
    \includegraphics[width=0.288\textwidth]{diagrams/aaa_V_1} & &
    \includegraphics[width=0.288\textwidth]{diagrams/aaa_V_3} \\
  \end{tabular}
  \caption{
    Sample diagrams of electroweak virtual corrections to triple 
    photon production.
    \label{fig:aaa:amps}
  }
\end{figure}

\begin{figure}[t!]
  \begin{tabular}{ccccc}
    \includegraphics[width=0.288\textwidth]{diagrams/aaW_V_2} & &
    \includegraphics[width=0.288\textwidth]{diagrams/aaW_V_1} & &
    \includegraphics[width=0.288\textwidth]{diagrams/aaW_V_3} \\
  \end{tabular}
  \caption{
    Sample diagrams of electroweak virtual corrections to diphoton 
    production in association with a lepton-neutrino pair.
    \label{fig:aaw:amps}
  }
\end{figure}

\begin{figure}[t!]
  \begin{tabular}{ccccc}
    \includegraphics[width=0.288\textwidth]{diagrams/aaZ_V_2} & &
    \includegraphics[width=0.288\textwidth]{diagrams/aaZ_V_1} & &
    \includegraphics[width=0.288\textwidth]{diagrams/aaZ_V_3} \\
  \end{tabular}
  \caption{
    Sample diagrams of electroweak virtual corrections to diphoton 
    production in association with a lepton-pair.
    \label{fig:aaz:amps}
  }
\end{figure}

\Sherpa, on the other hand, provides the tree-level matrix 
elements, infrared subtraction, process management and phase-space 
integration of all contributions to all processes considered in 
this publication through its tree-level matrix element generator 
\textsc{Amegic} \cite{Krauss:2001iv}. 
Its inbuilt infrared subtraction is performed in the QED 
generalisation of the Catani-Seymour scheme~\cite{Catani:1996vz,
  Dittmaier:1999mb,Gleisberg:2007md,Kallweit:2014xda,
  Kallweit:2015dum,Kallweit:2017khh,Schonherr:2017xxx}
and includes the appropriate initial state mass factorisation 
counter terms.
Both programs, \Sherpa and \GoSam, are interfaced through a 
dedicated interface based on the 
Binoth Les Houches Accord~\cite{Binoth:2010xt,Alioli:2013nda}. 
Cross-checks of the tree-level matrix elements of \GoSam and 
\Sherpa and the renormalized pole coefficients of the virtual 
corrections of \GoSam and the infrared poles of \Sherpa have 
been performed for several phase space points spanning 
multiple kinematic regimes and we have found excellent 
agreement.

This combination of tools was previously used to calculate the 
NLO QCD corrections to \ldots \cite{} and the 
NLO EW corrections to for $\gamma\gamma+0,1,2\,\text{jets}$ production 
in \cite{Chiesa:2017gqx}.
